### 2023-10-29 results/celegans.tex
changed table
removed useless files and todos

\begin{figure}[H]
  \centering
  \begin{tikztimingtable}%TODO change or find other way
    $e_0$       & x 4H    L 4H    N(A1) 3L N(A2) 4H    x\\
    $e_{next}$  & x 4L    H 4L    N(B1) 3H N(B2) 4L    x\\
    $e_{in}$    & x 4H    L 4H    N(C1) 3L N(C2) 4H    x\\
    $e_{out}$   & x 2H 2L L 2H 2L N(D1) 3L N(D2) 2H 2L x\\
    \extracode
    \node[gap, at={($(A1|-A2)!0.5!(A2)$)}];
    \node[gap, at={($(B1|-B2)!0.5!(B2)$)}];
    \node[gap, at={($(C1|-C2)!0.5!(C2)$)}];
    \node[gap, at={($(D1|-D2)!0.5!(D2)$)}];
    \tablerules
    \begin{pgfonlayer}{background}
      \vertlines[help lines]{0.55,4.55,5.55,9.55,12.55,16.55}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Flags time diagram for the celegans problem with $n_s=1$}
  \label{tim:airline}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \cellcolor[HTML]{808080}\acs{RMSE} & BD1 & LUAL & PVR & VB1\\
    \hline
    Sequence 5 & $5.02\cdot 10^{-2}$ & $1.68\cdot 10^{-1}$ & $1.32\cdot 10^{-1}$ & $5.07\cdot 10^{-2}$\\
    \hline
    Sequence 15 & $6.98\cdot 10^{-2}$ & $1.39\cdot 10^{-1}$ & $1.86\cdot 10^{-1}$ & $6.63\cdot 10^{-2}$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each neuron's prediction for the two selected sequences}
  \label{tab:celegansDigital}
\end{table}

>>>>

\begin{figure}[H]
  \centering
  \begin{tikztimingtable}
    $e_0$       & x 4H    L 4H    N(A1) 3L N(A2) 4H    x\\
    $e_{next}$  & x 4L    H 4L    N(B1) 3H N(B2) 4L    x\\
    $e_{in}$    & x 4H    L 4H    N(C1) 3L N(C2) 4H    x\\
    $e_{out}$   & x 2H 2L L 2H 2L N(D1) 3L N(D2) 2H 2L x\\
    \extracode
    \node[gap, at={($(A1|-A2)!0.5!(A2)$)}];
    \node[gap, at={($(B1|-B2)!0.5!(B2)$)}];
    \node[gap, at={($(C1|-C2)!0.5!(C2)$)}];
    \node[gap, at={($(D1|-D2)!0.5!(D2)$)}];
    \tablerules
    \begin{pgfonlayer}{background}
      \vertlines[help lines]{0.55,4.55,5.55,9.55,12.55,16.55}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Flags time diagram for the celegans problem with $n_s=1$}
  \label{tim:airline}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    \rowcolor{gray}
    Neuron & BD1 & LUAL & PVR & VB1\\
    \hline
    Sequence 5 & $5.02\cdot 10^{-2}$ & $1.68\cdot 10^{-1}$ & $1.32\cdot 10^{-1}$ & $5.07\cdot 10^{-2}$\\
    \hline
    Sequence 15 & $6.98\cdot 10^{-2}$ & $1.39\cdot 10^{-1}$ & $1.86\cdot 10^{-1}$ & $6.63\cdot 10^{-2}$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each neuron's prediction for the two selected sequences}
  \label{tab:celegansDigital}
\end{table}
